---
title: "Deaths By State"
author: "Alan Jackson"
date: "5/17/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)

path <-  "/home/ajackson/Dropbox/Rprojects/Covid/"

df <- read_csv(paste0(path, "MiscData/DeathsByState.csv"))

votes <- read_csv(paste0(path, "MiscData/Popular_vote.csv")) %>% 
  rename(State=state)

df <- left_join(df, votes, by="State")

knitr::opts_chunk$set(echo = TRUE)
```

##  Deaths by State as of May 17, 2021

Large variation by state. Part of that is that states that got hit early
tended to have very large death numbers, before various treatments and 
mitigation methods were discovered. Washington being an exception - even
though the first state to get the virus, the governor took strong, immediate
action and scrupulously followed the advice of health professionals.


```{r plot}

df %>% 
  ggplot(aes(y=DeathsPer100k, 
             x=reorder(State, DeathsPer100k), 
             label=State,
             fill=dem_percent)) + 
  geom_col() + 
  scale_fill_gradient2(low = "red", 
                       high = "blue", 
                       mid = "white", 
                       #limits=c(90,10),
                       midpoint = 50) + 
  coord_flip() + 
  labs(x="Deaths per 100,000",
       y="State",
       title="Total COVID Deaths per 100,000 by State")

df %>% 
  mutate(size=(dem_votes+rep_votes)/18000000) %>% 
  ggplot(aes(y=DeathsPer100k, 
             x=reorder(State, DeathsPer100k), 
             label=State,
             fill=size)) + 
  geom_col() + 
  scale_fill_gradient2(low = "red", 
                       high = "blue", 
                       mid = "white", 
                       limits=c(0,1),
                       midpoint = .20
                       ) + 
  coord_flip() + 
  labs(x="Deaths per 100,000",
       y="State",
       title="Total COVID Deaths per 100,000 by State")

df %>% 
  ggplot(aes(y=DeathsPer100k, 
             x=reorder(State, DeathsPer100k), 
             label=State)) + 
  geom_col() + 
  scale_fill_gradient2(low = "red", 
                       high = "blue", 
                       mid = "white", 
                       #limits=c(90,10),
                       midpoint = 50) + 
  coord_flip() + 
  labs(x="Deaths per 100,000",
       y="State",
       title="Total COVID Deaths per 100,000 by State")


```

Let's try a scatterplot instead

```{r scatter}

df %>% 
  ggplot(aes(y=DeathsPer100k, 
             x=dem_percent, 
             label=State,
             fill=dem_percent)) + 
  geom_point() + 
  scale_fill_gradient2(low = "red", 
                       high = "blue", 
                       mid = "white", 
                       #limits=c(90,10),
                       midpoint = 50) + 
  coord_flip() + 
  labs(y="Deaths per 100,000",
       x="Percent Democratic Vote",
       title="Total COVID Deaths per 100,000 by State")

```

What about deaths colored by ruralness?
